%!TEX program = xelatex
\documentclass[margin,line]{res}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

%\usepackage{MinionPro}
\usepackage{fontspec,hyperref}
\usepackage[none]{hyphenat}
\usepackage{hanging}

%\defaultfontfeatures{Path = /usr/local/texlive/2015/texmf-dist/fonts/opentype/public/fontawesome/}
\usepackage{fontawesome}

\usepackage{fancyhdr}

\fancyhf{}
\fancyfoot[C]{\hfill \footnotesize \today \ $\vert$ \thepage}
\renewcommand\headrulewidth{0pt}
\pagestyle{fancy}

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}

\begin{document}

\name{Stephen B. Holt \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
University at Albany, SUNY     & {\faPhone} (518) 442-3855\\            
Department of Public Administration and Policy   & {\faEnvelope} \href{mailto:sbholt@albany.edu}{sbholt@albany.edu} \\         
135 Western Ave. & {\faTwitter}  \href{https://twitter.com/SteveBHolt}{@SteveBHolt}\\       
Albany, NY 12203  & {\faGlobe} \href{https://stevebholt.github.io/}{https://stevebholt.github.io/} \\
 & {\faGlobe} \href{https://scholar.google.com/citations?user=VtRjfVkAAAAJ&hl=en}{Google Scholar}\\     
\end{tabular}

\section{\sc Research Interests}
Representative bureaucracy, prosocial motivation, education policy, civic behaviors
\vspace{.1in}

\section{\sc Education}
{\bf American University}, Washington, DC\\
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D., Public Administration, 2017
\begin{list2}
\vspace*{.05in}
\item[]Fields: Public Administration, Public Policy, Research Methods
\end{list2}
\end{list1}
\vspace*{-.1in}

{\bf George Washington University}, Washington, DC\\
\vspace*{-.1in}
\begin{list1}
\item[] Master of Public Policy, 2012
\end{list1}

{\bf University of Florida}, Gainesville, Florida\\
\vspace*{-.1in}
\begin{list1}
\item[] B.A., Political Science and English, 2009
\end{list1}

\section{\sc Academic Positions}
Associate Professor, \textbf{University at Albany, State University of New York}, Department of Public Administration \& Policy, 2017-present

\section{\sc Professional Research Experience}
\begin{hangparas}{.25in}{1}
Research Analyst, Westat, August 2011-August 2013
\begin{list1}
\item[] Research design team for Early Childhood Longitudinal Study, 2010 cohort.
\item[] Program evaluation team for the Ohio Teacher Incentive Fund.
\end{list1}

\end{hangparas}

\section{\sc Publications}
\textbf{Holt, Stephen B.} and Katie Vinopal. (2023). Examining Inequality in the Time Cost of Waiting. \href{https://doi.org/10.1038/s41562-023-01524-w}{\textit{Nature Human Behaviour}}.
\begin{itemize}
\item[] Media mentions: \href{https://www.economist.com/united-states/2021/05/08/black-americans-spend-more-of-the-day-being-kept-waiting}{The Economist}, \href{https://www.washingtonpost.com/business/another-sign-of-inequality-minutes-spent-waiting/2023/02/14/4579a0de-ac76-11ed-b0ba-9f4244c6e5da_story.html}{The Washington Post}, \href{https://www.newscientist.com/article/2358744-people-with-low-incomes-spend-longer-waiting-for-basic-services-in-us/}{New Scientist}, \href{https://www.theguardian.com/commentisfree/2023/feb/12/if-the-government-could-only-give-poorer-people-some-more-time}{The Guardian}, \href{https://www.bloomberg.com/opinion/articles/2023-02-14/waiting-at-the-counter-delays-add-up-by-income-race-and-zip-code}{Bloomberg News}
\end{itemize}

Sorensen C., Lucy, and \textbf{Stephen B. Holt}. (2021). Sorting it Out: The Effects of Intensive Charter Expansion on Teacher and Student Composition at Traditional Public Schools. \href{https://doi.org/10.1016/j.econedurev.2021.102095}{\textit{Economics of Education Review}}.

\textbf{Holt, Stephen B.} and Heasun Choi. (2020). When Knowing is Caring: Examining the Relationship Between Diversity Exposure and PSM. \href{https://doi.org/10.1177/0734371X20966652}{\textit{Review of Public Personnel Administration}}.

Piatak, Jaclyn and \textbf{Stephen B. Holt}. (2020). Disentangling Altruism and Public Service Motivation: Who Exhibits Organizational Citizenship Behaviour?. \href{https://doi.org/10.1080/14719037.2020.1740302}{\textit{Public Management Review}}.

Piatak, Jaclyn and \textbf{Stephen B. Holt}. (2019). Volunteering: A Matter of Altruism or Public Service Motivation? \href{https://doi.org/10.1093/jopart/muz041}{\textit{Journal of Public Administration Research and Theory}}.

Johnston, Jocelyn and \textbf{Stephen B. Holt}. (2019). Examining the Influence of Representative Bureaucracy in Public and Private Prisons. \href{https://doi.org/10.1111/psj.12367}{\textit{Policy Studies Journal}}.

AbouAssi, Khaldoun, Jasmine M. Johnson, and \textbf{Stephen B. Holt}. (2019). Job Mobility Among Millennials: Do They Stay or Do They Go? \href{https://doi.org/10.1177/0734371X19874396}{\textit{Review of Public Personnel Administration}}.

Vinopal, Katie and \textbf{Stephen B. Holt}. (2019). Rookie Mistakes: The Interplay of Professional Experience and Demographic Representation. \href{https://doi.org/10.3102/0013189X19867699}{\textit{Educational Researcher}}.
\begin{itemize}
\item[] Media Mentions: \href{https://www.aera.net/Newsroom/New-Research-Video-Recap-Rookie-Mistakes-The-Interplay-of-Teacher-Experience-and-Racial-Representation}{AERA News Release}
\end{itemize}

\textbf{Holt, Stephen B}. (2019). Giving Time: Examining sector differences in volunteering intensity. \href{https://doi.org/10.1093/jopart/muz007}{\textit{Journal of Public Administration Research and Theory}}, 30(1), 22-40.

Amirkhanyan, Anna A., \textbf{Stephen B. Holt}, Austin M. McCrea, and Kenneth J. Meier. (2018). Managing Racial Diversity: Matching Internal Strategies to Environmental Needs. \href{https://doi.org/10.1111/puar.12977}{\textit{Public Administration Review}}.

\textbf{Holt, Stephen B}. (2019). The influence of high schools on developing public service motivation. \href{https://doi.org/10.1080/10967494.2018.1470120}{\textit{International Public Management Journal}}, 22(1), 127-175.

\textbf{Holt, Stephen B}. (2018). For Those Who Care: The effect of Public Service Motivation on Sector Selection. \href{http://doi.org/10.1111/puar.12906}{\textit{Public Administration Review}}, 78(3), 457-471.

\textbf{Holt, Stephen B.}, and Seth Gershenson. (2019). The impact of teacher demographic representation on student attendance and suspensions. \href{http://doi.org/10.1111/psj.12229}{\textit{Policy Studies Journal}}, 47(4), 1069-1099.
\begin{itemize}
\item[] Media Mentions: \href{https://www.brookings.edu/blog/brown-center-chalkboard/2019/04/02/the-teacher-diversity-gap-is-literally-inherited/}{Brookings Institute}
\end{itemize}

Gershenson, Seth, \textbf{Stephen B. Holt}, and Nicholas Papageorge. (2016). Who Believes in Me? The Effect of Student-Teacher Demographic Match on Teacher Expectations. \href{https://doi.org/10.1016/j.econedurev.2016.03.002}{\textit{Economics of Education Review}}, 52, 209-224.

\begin{itemize}
\item[] Media mentions: \href{https://www.vox.com/policy-and-politics/2015/8/19/9178573/teacher-students-race-study}{vox.com}, \href{http://blogs.edweek.org/edweek/inside-school-research/2015/09/racial_mismatch_changes_teache.html?cmp=soc-edit-tw}{Education Week}, \href{http://www.upjohn.org/research-highlights/are-teachers\%E2\%80\%99-expectations-students-systematically-biased}{Upjohn Institute}, \href{https://www.washingtonpost.com/news/answer-sheet/wp/2017/04/09/study-black-students-from-poor-families-are-more-likely-to-graduate-high-school-if-they-have-at-least-one-black-teacher/?utm_term=.38baf7bc6467}{Washington Post}, \href{https://www.nytimes.com/2019/01/15/upshot/the-gender-achievement-gap-starts-later-for-asian-american-students.html}{New York Times}, \href{https://www.forbes.com/sites/nataliewexler/2018/09/14/why-we-need-a-teacher-workforce-thats-both-diverse-and-knowledgeable/#4f36a3407f3c}{Forbes}, \href{https://openknowledge.worldbank.org/handle/10986/29883}{World Bank}, \href{https://www.brookings.edu/research/high-hopes-and-harsh-realities-the-real-challenges-to-building-a-diverse-teacher-workforce/}{Brookings Institute}
\end{itemize}

Gershenson, Seth, and \textbf{Stephen B. Holt}. (2015). Gender Gaps in High School Students’ Homework Time. \href{http://journals.sagepub.com/doi/full/10.3102/0013189X15616123}{\textit{Educational Researcher}}, 44(8), 432-441.

\section{\sc Under Review}
\textbf{Holt, Stephen B.}, Rui Wang, and Seth Gershenson. ``Stress Test: Examining the Evolution of Teachers' Mental Health." (under review).

Gershenson, Seth, \textbf{Stephen B. Holt}, and Adam Tyner. ``Making the Grade: The effect of teacher grading standards on student outcomes." (under review).

\textbf{Holt, Stephen B.}, Katie Vinopal, Heasun Choi, and Lucy C. Sorensen. \href{https://doi.org/10.26300/meqn-w550}{``Strictly Speaking: Examining Teacher Use of Punishment on Student Outcomes."} (under review).

\textbf{Holt, Stephen B.} and Jaclyn S. Piatak. ``Attraction or Socialization? Examining the relative effects of sector and public service motivation on prosocial behavior." (under review).

\section{\sc Books}
Piatak, Jaclyn, and \textbf{Stephen B. Holt}. (2021). \href{https://doi.org/10.1017/9781108966672}{\textit{Public Service Motivation and Public Opinion: Examining Antecedents and Attitudes}}. Cambridge Elements Series. Cambridge University Press: Cambridge, UK.

\section{\sc Book Chapters}
Holt, Stephen B. (2022). ``Teacher Motivation and Accountability Policy Design." In \textit{The Handbook of Research on Motivation in Public Administration}. Eds. Randall S. Davis and Edmund C. Stazyk. Edward Elgar Publishing: Cheltenham, UK.

Gershenson, Seth, and \textbf{Stephen B. Holt}. (2021). ``Chapter 5: Time-use data reveals gender differences in out-of-school learning." In \href{https://www.unescap.org/kp/2021/harnessing-time-use-data-evidence-based-policy-2030-agenda-sustainable-development-and}{\textit{Harnessing Time-Use Data for Evidence-based Policy, the 2030 Agenda for Sustainable Development and the Beijing Platform for Action}} Eds. Michael Bittman and Maria Floro. United Nations Economic and Social Commission for Asia and the Pacific: Bangcock, Thailand.

\section{\sc Honors and Awards}
2022 Best Public Sector Human Resources Book Award, American Society for Public Administration, Section on Personnel Administration and Labor Relations

2018 Finalist for Best Dissertation Award for the Public and Nonprofit Division, Academy of Management

2016 Staats Emerging Scholar Award, NASPAA

2016 Neil and Ann Kerwin Doctoral Dissertation Fellowship, American University - \$10,000

2016 Charles H. Levine Doctoral Research Award, American University

\section{\sc Grants}
Fall 2020 Spencer Foundation Research Communications Grant Award (with Seth Gershenson) - \$15,000 (Awarded Spring 2021)

\section{\sc Conference Papers}
\begin{hangparas}{.25in}{1}
2022: Association for Education Finance and Policy Annual Conference; Association for Public Policy Analysis and Management Annual Meeting

2021: Association for Education Finance and Policy Annual Conference

2020: Association for Public Policy Analysis \& Management International Conference

2019: Association for Education Finance and Policy Annual Conference; Public Management Research Association Annual Meeting; Elevating Public Service Motivation Conference

2018: American Society for Public Administration Annual Meeting; Association for Education Finance and Policy Annual Conference; Midwest Political Science Association Annual Conference; International Research Society for Public Management Annual Conference; Association for Public Policy Analysis \& Management International Conference

2017: Association for Budgeting and Financial Management Annual Meeting;  American Political Science Association Annual Meeting; Public Management Research Association Annual Meeting

2016: Association for Public Policy Analysis and Management Annual Meeting; American Political Science Association Annual Meeting; Midwest Political Science Association Annual Meeting

2015: Association for Public Policy Analysis and Management Annual Meeting; American Political Science Association Annual Meeting; National Education Finance Conference Annual Meeting

2014: Eastern Economic Association Annual Meeting
\end{hangparas}

\section{\sc Teaching Experience}
\subsection{\sc Graduate Courses}
\vspace*{-.1in}
Intro. to the Foundations of Public Administration (MPA) (in-person and online), University at Albany - SUNY, Fall 2017, Spring 2018, Fall 2018 (2 sections), Spring 2019, Fall 2019 (Online), Fall 2020 (Online), Fall 2021 (Online), Spring 2022

Scholarly Foundations of Politics and Administration (Ph.D.), University at Albany - SUNY, Spring 2019, Fall 2020, Fall 2021

\vspace*{-.1in}
\subsection{\sc Undergraduate Courses}
\vspace*{-.1in}
Methodological Tools in Public Policy, University at Albany - SUNY, Fall 2019, Spring 2020, Spring 2022

Public Administration and Management, University at Albany - SUNY, Fall 2017

\vspace*{-.1in}
\subsection{\sc Undergraduate Courses, Other Institutions}
\vspace*{-.1in}
Administrative Politics, American University, Spring 2015

\vspace*{-.1in}
\subsection{\sc Doctoral Candidacy Committees}
\vspace*{-.1in}
2021-current: Arzana Myderrizi (\textit{member})\\
2020-current: Soohyun Park \textit{member})\\
2020-current: Jisang Kim (\textit{member}\\
2019-current: Haelee Kim (\textit{member})\\
2018-current: Heasun Choi (\textit{co-chair})\\

\vspace*{-.1in}
\subsection{\sc Undergraduate Honors Theses}
\vspace*{-.1in}
2018-2019: Carly Dettman, ``A Descriptive Analysis of Segregation within Schools" (\textit{chair})\\

\vspace*{-.1in}
\subsection{\sc Other Academic Advising}
\vspace*{-.1in}
2017-current: Academic Adviser for MPA, Certificate of Graduate Studies, and non-degree graduate students\\

\section{\sc Professional Service}
Reviewer: {\em Journal of Public Economics} (1), {\em Public Administration Review} (6), {\em Journal of Public Administration Research and Theory} (9), {\em Educational Evaluation and Policy Analysis} (4), {\em American Review of Public Administration} (1), {\em The Elementary School Journal} (3), {\em Economics of Education Review} (3), {\em Policy Studies Journal} (1), {\em International Public Management Journal} (16), {\em Public Personnel Management} (4), {\em Public Management Review} (6), {\em Education Economics} (1), {\em AERA Open} (6), {\em Studies in Educational Evaluation} (4), {\em Review of Public Personnel Administration} (4), {\em Education Policy Analysis Archives} (1), {\em International Review of Administrative Sciences} (2), {\em International Journal of Public Administration} (1), {\em Journal of Public and Non-Profit Affairs} (1), {\em Journal of Teacher Education} (1), {\em Perspectives on Public Management and Governance} (1), {\em Public Administration} (1), {\em PLOS One} (2), {\em Public Administration Quarterly} (1), {\em Public Performance \& Management Review} (1).\\

AOM Public and Non-profit Best Article Selection Committee: Member (2022, 2023)

APPAM Public and Non-profit Finance and Management Section: Co-Chair (2023)

\section{\sc Departmental Service}
2021-current: MPA Program Committee\\
2021-2022: Junior Representative, Executive Committee\\
2021-current: Co-chair, Northeast Conference of Public Administration Organizing Committee\\
2018-current: Chair, NASPAA Competency Self-Assessment Committee\\
2017-current: Member, MPA Admissions Committee\\
2019: Member, Ph.D. Admissions Sub-Committee, Public Management Concentration\\
2017-current: Member, Welcome Week Math Team\\
2017-current: MPA Student Adviser\\
2017-current: Faculty Adviser, Generation Vote, University at Albany chapter\\
Fall 2018: Volunteer, Food for Finals\\

\section{\sc Professional Memberships}
American Political Science Association \\
American Society for Public Administration \\
Association for Public Policy Analysis and Management \\
Public Management Research Association

\end{resume}
\end{document}



